Distributed Version Control Systems

### 2010-05-16 paper.tex
Renombrada la seccion Should I use it in my project
Mi nombre estaba mal escrito :(
modificada introduccion y agregada seccion de historia

%It is given that, in these times, modern software projects need a tool to 
%automatically track changes made in the source files, called Version Control Systems (VCS).

\PARstart Version Control Systems (VCS) usually track the whole history of the
source code in a central server that everyone that can access. This 
central server contains all the changes and branches of the code and 
the users that can read the versions or commit changes have to connect 
to this repository. The most popular today example of this approach is SVN, which is a 
widely used VCS.

Distributed Version Control Systems (DVCS) are a modern way of managing
revisions of software that do not have a centralized server, for this reason 
they are also called De-centralized Version Control Systems. Everybody has a 
copy of the full repository with all changes made in the history.

@@

We're going to do a comparison between centralized and decentralized control version systems,
highlighting the differences and advantages and disadvantages of both approachs in various 
contexts, both on a conceptual and practical level. In this paper we'll base our explanations 
on Git but there are no big differences between 
most of these DVCS, especially between Git and Mercurial that are largely similar, with 
most commands having the same names in both tools.

@@

>>>>

% Un detalle que yo corregiría es la Introducción, creo que se  mezclan cosas con diferente 
% nivel de detalle, entonces propondría hacer una intro de muy alto nivel, que se concentre 
% en contar el problema y describir el objetivo del artículo.
% Por otro lado la reseña histórica iría en una sección aparte.

\PARstart Most software projects use Version Control Systems (VCS) to manage revisions
of source code. 
Version Control Systems traditionally track the whole history of the
source code in a central server that everyone that can access. 
%This central server contains all the changes and branches of the code and 
%the users that can read the versions or commit changes have to connect 
%to this repository. 
Users need to access this central server to work with their VCS.
A modern, different approach of doing revision control is using a \emph{Distributed} Version Control System (DVCS).
In these systems, there is no central server that contains the history and tracks changes,
instead everyone has a copy of the full repository with the complete history.
Given the lack of a centralized server they are also called De-centralized Version Control Systems.

In this paper we're going explain what DVCS are, based on the distributed system Git, 
and compare them to centralized Version Control Systems,
highlighting the differences, advantages and disadvantages of both approachs in various 
contexts, in a both a conceptual level, and a practical level of actual VCS; ultimately 
evaluating when to use or not Distributed Version Control Systems.

% Explain DVCS, particulary GIT
% Comparison between DVCS and CVCS
% When we should or we shouldn't use it.

@@

@@

\section{DVCS history}

For reference, in this paper we'll base our explanations on Git but for most features there 
are no big differences between most of these DVCS, especially between Git and Mercurial which are 
largely similar, with most commands having the same names in both tools.
